Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-05-09 research_proposal/research_proposal_draft.qmd
putting OLS and WLS into appendix

The choice of $\boldsymbol{G}$ determines the composition of reconciled forecasts $\tilde{\boldsymbol{y}}_h$. Methods are developed to estimate $\boldsymbol{G}$, the first attempts at least squares forecast reconciliation were made by @Hyndman2011-jv.

They proposed the optimal $\boldsymbol{G}$ based on the regression model:

@@

>>>>

The choice of $\boldsymbol{G}$ determines the composition of reconciled forecasts $\tilde{\boldsymbol{y}}_h$. Methods are developed to estimate $\boldsymbol{G}$, including the OLS and WLS developed by @Hyndman2011-jv and @Hyndman2016-ic, respectively. A more detailed explanation of these methods can be found in the @sec-ols-wls Appendix.

@@

## OLS and WLS Reconciliation {#sec-ols-wls}

The first attempts at least squares forecast reconciliation were made by @Hyndman2011-jv. They proposed the optimal $\boldsymbol{G}$ based on the regression model:
